Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-10 vesicle_code/docs/adhesion/adhesion.tex
worked on shear example

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
  \todo[inline]{Make black marks larger and reference that they come
  from Ghigliotti, Biben, Misbah 2010 JFM}
\end{figure}
\todo[inline]{Do the smaller reduced area doublets since the intrinsic
viscosity seemed to increase as the reduced area was decresed further}
\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
adhesion and due to the bending/tension}

>>>>

In the left plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare
the intrinsic viscosity of a single tank treading vesicle to a doublet.
To validate our simulations, we superimpose (black marks) the intrinsic
viscosity calculated by Ghigliotti et
al.~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
significant increases the intrinsic viscosity at all reduced areas.  To
further characterize the effect of adhesion, in the right plot of
Figure~\ref{fig:shearIntrinsicViscosity} we decompose the intrinsic
viscosity into the contributions from the bending and tension, and the
contribution from the adhesion.  We see that the effect of the adhesion
on the intrinsic viscosity is largest for vesicles with small reduced
areas.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
  viscosity of a tank treading vesicle (blue) and a doublet (red).  The
  shear rate is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$,
  and the adhesion length scale is $\delta = 0.4$.  The length of the
  vesicles at each of the reduced areas is fixed, while the area changes
  with differing reduced areas.  The black marks denote intrinsic
  viscosity values computed by Ghigliotti et
  al.~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em Right}:
  The decomposition of the intrinsic viscosity into the contributions
  for the bending and tension of the vesicles, and the contribution from
  the vesicle adhesion.}
\end{figure}
